---
title: "Global Temperature Anomalies"
subtitle: "A visualization of NASA's GISTEMP anomaly data"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
source(".././R/gtaviz.R")
```

**Author:** [Matthew Hoff](https://github.com/mghoff)
<br/>
**License:** [MIT](https://opensource.org/licenses/MIT)
<br/>

[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/)

Below is a visual representation of the Global Monthly Means-Anomalies for the Combined Land-Surface Air &
Sea-Surface Water Temperature data, as provided by
[NASA's GISS Surface Temperature Analysis (GISTEMP)](https://data.giss.nasa.gov/gistemp/),
where "anomaly" is defined as the deviation from the long term (1951-1980) mean in degrees Celsius.

## {.tabset}

### Heatmap

```{r heat, echo=FALSE, warning=FALSE, out.width="100%"}
p1
```

### Line Plot

```{r time, echo=FALSE, warning=FALSE, out.width="100%"}
p2
```

## {-}

Source: `r url`

Last updated on `r format(as.POSIXct(Sys.time()), "%A, %B %d at %H:%M:%S", tz = "America/New_York", usetz = TRUE)`.
